Curriculum and Imitation Learning for Biped Locomotion on Rough Terrain

### 2019-02-02 paper/rss/main.tex
Add abstract

\begin{abstract}
The abstract goes here.
\end{abstract}

@@

Results on the 2D-Hard environment are shown in Fig. \ref{fig:nocur baseline}.
Like in Fig. \ref{fig:rs baseline},
we plot the median reward and 5th/95th percentiles over 32 testing episodes.

>>>>

\begin{abstract}
  Biped locomotion with precise foot placement has previously been achieved only for static gaits, using detailed dynamics models and hierarchical optimization-based planning.
  Meanwhile, learning-based approaches to locomotion, such as deep reinforcement learning, are still too sample-inefficient to achieve the precise foot placement necessary to traverse rough terrain.
  In this paper, we improve sample efficiency for learning-based control techniques.
  Our strategy applies to any periodic robotic control task that admits significant prior knowledge.
  First, we engineer a versatile low-level policy (a.k.a. trajectory generator) with interpretable high-level parameters.
  Second, we use reward shaping, imitation learning, and curriculum learning to train a high-level policy for the control task.
  We evaluate this technique with a simulated biped locomotion task over rough terrain.
  To the best of our knowledge, our experiments are the first to achieve such precise foot placement
  using a fast, non-static gait that requires no optimization during policy execution.
\end{abstract}

@@

Results on the 2D-Hard environment are shown in Fig. \ref{fig:nocur baseline}.
Like in Fig. \ref{fig:ars baseline},
we plot the median reward and 5th/95th percentiles over 32 testing episodes.
